---
title: "Vignette"
author: "Gianluca Lelli"
date: "2024-05-16"
output:
  html_document: default
  pdf_document: default
---
# My first markdown file!
This file contains functions for R scripting in Geo-Ecological Remote Sensing

We are going to make use of following packages:

```{r}
library(imageRy)
library(terra)
library(viridis)
```

In order to visualize the list of data use:

```{r, eval=TRUE}
im.list()
```


In order to import data we can use the following function:

```{r, eval=TRUE}
mato=im.import("matogrosso_l5_1992219_lrg.jpg")
```

This plot is related to the following bands: band 1 = NIR, band 2 = red, band 3 = green.
We can change the visulization by changing the order of bands in the RGB space, as:

```{r, eval=TRUE}
im.plotRGB(mato, 2,1,3)
```
In order to look at different band combinations altogether we can use :
```{r, eval=TRUE}
par(mfrow=c(1,3))
im.plotRGB(mato, 1,2,3)
im.plotRGB(mato, 2,1,3)
im.plotRGB(mato, 3,2,1)
```


##Calculating spectral indices
```{r, eval=TRUE}
dvi <- mato[[1]]-mato[[2]]
plot(dvi, col=viridis(100))
```

Calculating variability:
```{r, eval=T}
sd5 <- focal(mato[[1]], matrix(1/25, 5, 5), fun=sd)
plot(sd5, col=magma(100))
```
